### 2020-01-14 sections/discussion.tex
update results

% !TEX root = ../main.tex
This paper presented a new Bayesian approach to estimate galaxy pitch angle, making use of citizen science results to measure spiral arms through photometric modelling. We introduce an adaptation of the Anderson-Darling test to incorporate full Bayesian posterior probabilities and utilize this test to investigate theories governing spiral formation and evolution.

The statistical approach implemented in this paper allows a more thorough approach than calculating length-weighted pitch angles, and better accounts for inter-arm pitch angle variation than fourier analysis. \comment{This is a strong statement, how can we quantify it?}.

@@

This work is primarily held back by the sample used; due to time constraints the \textit{Galaxy Builder} galaxies used are not guaranteed to be representative. A larger and more complete sample is needed to be fully confident in our results, but we are confident that the methodlogy proposed here is a scalable solution to the problems facing investigation of spiral morphology.

>>>>

% !TEX root = ../main.tex
This paper presents a new Bayesian approach to estimate galaxy pitch angle, making use of citizen science results to measure spiral arms through photometric modelling. We introduce an adaptation of the Anderson-Darling test to incorporate full Bayesian posterior probabilities and utilize this test to investigate theories governing spiral formation and evolution.

The statistical approach implemented in this paper allows a more thorough examination of pitch angle than simpler methods of logarithmic spiral fitting, and better accounts for inter-arm pitch angle variation than fourier analysis \comment{This is a strong statement, how can we quantify it?}.

@@

This work is primarily limited by the sample used; due to time constraints the \textit{Galaxy Builder} galaxies used are not guaranteed to be representative. A larger and more complete sample is needed to be completely confident in our results. However, we believe that the methodlogy proposed here is a scalable solution to the problems facing investigation of spiral morphology.

### 2020-01-14 sections/method.tex
update results

% !TEX root = ../main.tex
\subsection{The Galaxy Sample}
The galaxies selected analysed in this paper are the 198 galaxies from \comment{Lingard et al, in prep.}. We combine classifications of galaxies which were repeated in the \textit{validation subset} with the original classifications, and perform clustering and point cleaning as detailed in \comment{Lingard et al, in prep.}. We remove any galaxies for which no arms were identified. This results in a hierarchiacal data structure of 109 galaxies, 250 spiral arms and 307,861 points in polar coordinates. We apply a scaling to the radius to unit variance (which does not impact log spiral pitch angle due to its scale invariance).

>>>>

% !TEX root = ../main.tex
\subsection{The Galaxy Sample}
The galaxies selected analysed in this paper are the 198 galaxies from \comment{Lingard et al, in prep.}. We combine classifications of galaxies which were repeated in the \textit{validation subset} with the original classifications. Clustering of drawn spiral arms and cleaning of points was then performed as detailed in \comment{Lingard et al, in prep.}. We remove any galaxies for which no arms were identified. This results in a hierarchiacal data structure of 109 galaxies, 250 spiral arms and 307,861 points.

Spiral arm points are deprojected to a face-on orientation using the position angle \textsc{PETRO\_PHI90} and axis ratio \textsc{PETRO\_BA90} keywords from the NASA-Sloan Atlas \comment{citation}. We scale the radii to have unit variance (which does not impact log spiral pitch angle due to its scale invariance).

### 2020-01-14 sections/results.tex
update results

% !TEX root = ../main.tex

@@

\begin{figure*}
  \includegraphics[width=17.7cm]{plots/cot_uniform_marginalized_tests.pdf}
  \caption{The results of a marginalized Anderson-Darling test (top panel), with confidence intervals shown, and marginalized Kolmogorov-Smirnov test p-values (lower panel). Moving rightwards on the x-axis implies greater confidence in rejecting the null hypothesis.}
  \label{fig:ad-cot-test}
\end{figure*}

\subsection{Dependence of pitch angle on Galaxy Morphology}
\label{section:morphology_comparision}
\subsubsection{Pitch angle vs. Bulge size}
We see no correlation between galaxy pitch angle derived from the \textit{hierarchial normal model} and Galaxy Zoo 2's debiased \citep{Willett2013:1308.3496v2} \textit{pbulge}, which has been shown to be a good measure of bulge size.

@@

\subsubsection{Pitch angle vs. Bar Strength}
We see no correlation between galaxy pitch angle derived from the \textit{hierarchial normal model} and Galaxy Zoo 2's debiased \textit{pbar}, which is widely viewed as a good measure of bar strength, and therefore a measure of the torque applied on the disc gas.

Separating the sample based off of $\mathrm{\textit{pbar}} > 0.5$, and restricting to galaxies with more than 10 classifications for \textit{pbar} (as performed by \citealt{2011MNRAS.411.2026M} and \citealt{2017MNRAS.469.3363K}) and performing a marginalized two-sample Anderson-Darling test does not find that the samples were drawn from different distributions.

>>>>

% !TEX root = ../main.tex
\subsection{Constraints on Galaxy Pitch angle}
Our hierarchical model can predict individual arm pitch angle with a hich degree of certainty, however it returns a large spread of potential values for the pitch angles of arms

@@

\begin{figure*}
  \includegraphics[width=17.7cm]{plots/cot_uniform_marginalized_tests.pdf}
  \caption{The results of a marginalized Anderson-Darling test (top panel), with values corresponding to various confidence intervals shown, and marginalized Kolmogorov-Smirnov test p-values (lower panel). Moving rightwards on the x-axis implies greater confidence in rejecting the null hypothesis.}
  \label{fig:ad-cot-test}
\end{figure*}

\subsection{Dependence of pitch angle on Galaxy Morphology}
\label{section:morphology_comparision}
\subsubsection{Pitch angle vs. Bulge size}
We see no correlation between galaxy pitch angle derived from the \textit{hierarchical normal model} and Galaxy Zoo 2's debiased \citep{Willett2013:1308.3496v2} \textit{pbulge}, which has been shown to be a good measure of bulge size.

@@

\subsubsection{Pitch angle vs. Bar Strength}
We see no correlation between galaxy pitch angle derived from the \textit{hierarchical normal model} and Galaxy Zoo 2's debiased \textit{pbar}, which is widely viewed as a good measure of bar strength, and therefore a measure of the torque applied on the disc gas.

Separating the sample based off of $\mathrm{\textit{pbar}} > 0.5$, and restricting to galaxies with more than 10 classifications for \textit{pbar} (as performed by \citealt{2011MNRAS.411.2026M} and \citealt{2017MNRAS.469.3363K}) and performing a marginalized two-sample Anderson-Darling test does not find that the samples were drawn from different distributions. \comment{Talk about number of galaxies in each sub-sample?}
